Mire microclimate: groundwater buffers temperature in waterlogged versus dry soils

### 2020-10-11 README.Rmd
Revert "Revert "readme picture""
This reverts commit 3dbc162c5e3a7bbd5851d52ce93ff214dbafaa5d.
updated links

![Alkaline fen in the Cantabrian Mountains](data/Sierra Cebolleda.JPG)

@@

This repository stores all the information related to the publication *Mire microclimate: groundwater buffers temperature in waterlogged versus dry soils*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the manuscript.

@@

* `data` Original raw files including soil temperature recording.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including clean data and figures.
* `src` Scripts in `R` language used to clean the raw data and perform the analyses of the manuscript.

@@

Please cite the dataset as `CITATION`

>>>>

![Alkaline fen in the Cantabrian Mountains](data/Sierra Cebolleda.jpg)

@@

This repository stores all the information related to the publication *Mire microclimate: groundwater buffers temperature in waterlogged versus dry soils*, including the raw datasets, the scripts to perform data cleaning and analysis, and the `Rmarkdown` files to create the [manuscript](https://github.com/efernandezpascual/mires/blob/master/doc/manuscript.md).

@@

* `data` Original raw files including soil temperature recording.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including clean data and figures.
* `src` Scripts in `R` language used to clean the raw data and perform the analyses of the [manuscript](https://github.com/efernandezpascual/mires/blob/master/doc/manuscript.md).

@@

Please cite any use of this repository as `Fernández-Pascual, E. & Correia-Álvarez., E. (2021). Mire microclimate: groundwater buffers temperature in waterlogged versus dry soils. International Journal of Climatology, in press.`

### 2020-10-11 doc/manuscript.Rmd
updated links

To test if the differences between dry and waterlogged points were significant, we used paired t-tests (n = 8 paired sites per each of the four bioclimatic variables). Tests were one-tailed, according to the original hypotheses: the dry point would have a higher diurnal range, a higher maximum temperature, a lower minimum temperature, and a higher annual range. To compare our soil measurements with the CHELSA air temperatures we calculated Pearson's correlation between both sets of values, and we also calculated the root-mean-square error (RMSE) of the CHELSA values as a measure of their accuracy (n = 8 sites per combination of bioclimatic variable and dry/waterlogged condition). We calculated RMSE using its implementation in the package *Metrics* [@RN4941]. We checked whether our data complied with the normality assumption of the t-test and Pearson's correlation using the Shapiro-Wilk normality test; the assumption was met in all cases (p > 0.05). To check whether the analyses were influenced by the fact that recording periods did not match across all eight sites, we repeated the analyses using only full-year, contemporaneous data series (01 Jan 2015 - 31 Dec 2017, excluding La Vega Comeya); the results of these analyses were the same as the ones presented in this article (Supplementary **Tables S1** and **S2**).

@@

*Tables S1-S2* Results of the statistical analyses, repeated using only the contemporaneous full-year data series.

>>>>

To test if the differences between dry and waterlogged points were significant, we used paired t-tests (n = 8 paired sites per each of the four bioclimatic variables). Tests were one-tailed, according to the original hypotheses: the dry point would have a higher diurnal range, a higher maximum temperature, a lower minimum temperature, and a higher annual range. To compare our soil measurements with the CHELSA air temperatures we calculated Pearson's correlation between both sets of values, and we also calculated the root-mean-square error (RMSE) of the CHELSA values as a measure of their accuracy (n = 8 sites per combination of bioclimatic variable and dry/waterlogged condition). We calculated RMSE using its implementation in the package *Metrics* [@RN4941]. We checked whether our data complied with the normality assumption of the t-test and Pearson's correlation using the Shapiro-Wilk normality test; the assumption was met in all cases (p > 0.05). To check whether the analyses were influenced by the fact that recording periods did not match across all eight sites, we repeated the analyses using only full-year, contemporaneous data series (01 Jan 2015 - 31 Dec 2017, excluding La Vega Comeya); the results of these analyses were the same as the ones presented in this article ([Supplementary **Tables S1** and **S2**](https://github.com/efernandezpascual/mires/blob/master/doc/supplementary.md)).

@@

[**Tables S1-S2**](https://github.com/efernandezpascual/mires/blob/master/doc/supplementary.md) Results of the statistical analyses, repeated using only the contemporaneous full-year data series.
